\chapter{Overview}\label{ch:gameModeOverview}
\section{Combat, Adventuring and Social.}\label{sec:gameModeList}
\begin{itemize}
	\item \textcolor{red}{\textbf{Combat}} Whenever an encounter is solved by attacking someone and directly harming them, it should be considered combat.
	When a trap is laid, or the characters try to defeat enemies by pushing a boulder onto them, it is adventuring instead.

	\item \textcolor{green}{\textbf{Adventuring}} is the sum amount of exploration, navigation, and survival.
	Whenever characters try to sneak by enemies, find their way around a massive ravine or create a distraction for a group of enemies, they're engaged in Adventuring.

	\item \textcolor{blue}{\textbf{Social}} is interacting with other (at least somewhat) intelligent creatures in non-violent ways.
	This includes diplomacy, haggling, perceiving information about others, subterfuge and threats, but ít doesn't include stealth (but does include disguise) or illusion. 
	Neither does it include a feint or trick during combat.

	\item \textcolor{orange}{\textbf{Crafting}} is special in that it doesn't actually resolve encounters, but is used by characters to create objects from base materials.
	As a result, Crafting is only tracked if a character has a crafting perk.
	A character also gains XP differently while crafting.
	For more information, see~\nameref{ch:crafting}.
	
\end{itemize}

The GM should make sure that the distinction between the Game Modes is clear. 
Whenever the encounter involves the environment and the characters aren't directly interacting with other creatures, it's an Adventuring encounter.
If the characters are talking or communicating directly with non-player creatures, it's a Social encounter.
If the characters are hostile towards creatures, they're in a combat encounter.
An action's Game Mode is not determined by the hurdle designed by the GM or laid out in a pre-made adventure, but by the action of the Group.

Of course, not every encounter can be resolved by every type of Game Mode. 
While it is entirely possible to sneak past a group of enemies or intimidate into letting you pass, it may not be possible to resolve a mystery-murder-case by Combat.

\section{Rewards}\label{sec:rewards}
When succeeding to overcome an encounter, the party should be rewarded in two major ways: Loot and Levels.

\subsection{Levels}\label{subsec:levels}
A character’s basic abilities are tracked for each of the Game Modes.
For overcoming an encounter thanks to a Game Mode, a character can gain 1 to 3 XP in that Game Mode, depending on the challenge’s importance, difficulty, and how well the characters handled it.
The level that character has in a Game Mode is derived from the amount of XP the character they have collected (see table below), starting at Level 1/0 XP for each Game Mode.
What constitutes as challenge for a Game Mode is described in each of the Mode descriptions.

Generally speaking, a character can gain double the XP if they handle the challenge in another Game Mode.

A character can add the Game Mode Level to a check in the Game Mode.
For example, in Combat, a weapon attack roll for an attack is \\
\begin{center}
	
1D20 + Attribute + Combat Level + MODS\\

\rowcolors{2}{lightgray}{white}
\begin{tabular}{r r | r r}
Level & XP & Level & XP\\ \hline
2 & 1 & 12 & 221\\
3 & 5 & 13 & 265\\
4 & 13 & 14 & 313\\
5 & 25 & 15 & 365\\
6 & 41 & 16 & 421\\
7 & 61 & 17 & 481\\
8 & 85 & 18 & 545\\
9 & 113 & 19 & 613\\
10 & 145 & 20 & 685\\
11 & 181 & 21 & 761\\
\end{tabular}\\~\\

\end{center}

\subsubsection{Tiers of Play}\label{subsubsec:tiersOfPlay}
A long-form adventure moves through multiple stages.
In these different tiers, the difficulty of challenges, the stakes of failure and the rewards, both fame and fortune, that the party receives, increase.
One example of this is, that the monsters in the Creature Compendium, are organized into Tiers of Play.
The following list is a list of some of these Tiers, along with the level range that they are usually associated with.
Usually, when determining what Tier of Play a group belongs to, you should look at the individual Game Level.
However, to determine the general feeling of the Adventure, it may be useful to just look at the highest level that the characters have.

\begin{itemize}
	\item Tier 1: Humble Beginnings (Level 1--2)
	\item Tier 2: Local Heroes (Level 3--4)
	\item Tier 3: Heroes of the Province (Level 5--6)
	\item Tier 4: Heroes of the Realm (Level 7--8)
	\item Tier 5: Heroes of the World (Level 9+)
\end{itemize}


\subsection{Gaining LP}\label{subsec:gainingLP}

Whenever a character gains XP, they also gain Learning Points.
The rate at which they gain Learning Points increases with the specific level in which they gained XP.\\
The formula for this is\\

\begin{center}
	LP gained = Specific Level x XP gained  x 100
\end{center}

This means that a character of combat level 3, who gained 1 combat XP after finishing a fight gains 300 Learning Points for doing so.
If the combat was hard, or this specific character contributed significantly to the fight, they might gain 2 XP, which means they would gain 600 Learning Points instead.\\

\subsection{Loot}\label{subsec:loot}
Loot is a form of itemized reward, that the players gain from succeeding in encounters.
This does not mean that loot is rewarded immediately, or that it always has to be rewarded, but that there is simply the opportunity to find loot.
Loot can be a treasure horde, the pocket money of a beaten enemy, a strong weapon, body parts that can be sold or used for alchemy or crafting, a reward from a patron or quest-giver, a perk source written on an ancient tablet, etc.
In general, a GM should distribute Loot in an adventure by using the following rules:
\begin{itemize}
	\item The amount of loot of an encounter should be equal to about 150 Gold times the average level of the encounter tier.
	If an encounter rewards more than one XP, the Gold Value of that encounter should also be multiplied by the amount of XP
	For example, a regular Tier 3 encounter should be worth about 825 Gold.
	\item Regarding Combat, enemies have loot tables (that a character can access via examination or butchering).
	These should count for about half of that enemy's loot value.
	If half or less of the enemies in an encounter have a loot table, it should be a fourth.
	\item Objects that aren't forms of currency are worth half of their base value.
	\item Required (and expected) encounters are worth their full value.
	\item Encounters that are optional, but difficult, should be worth their full value.
	\item Encounters that are needed to access large parts of the loot should be worth their full value.
	\item Encounters that are optional, happen randomly, or are so easy they don't reward XP, should not be worth anything.
	In such cases, the loot tables are more than enough.
\end{itemize}


%Theoretically, a character can reach higher levels than 21 (however, this requires a lot %of playing). When calculating the XP cost for these cases, use the following formula:\\

%XP needed = (XP needed for last level) + (last level * 4)\\~\\

%Or, if you don't like recursive functions:\\
%XP needed for a level = 2 * (level - 1) * level + 1\\~\\

%Also, the formula for the current level derived from your XP is:\\

%Level = floor (1/2 + (SQRT(2*XP - 1)  + 1)\\