\chapter{Crafting}\label{ch:crafting}
Crafting acts as a fourth Game Mode.
A character can use crafting perks to create their own potions, weapons and armor, or enchant objects.
Once a character has gained at least one rank in a crafting perk, they start to track Crafting Levels.\\
A character can add their crafting level to appropriate checks made to harvest ingredients and craft items if they have the appropriate perks.\\
To advance in crafting, a character has to harvest and craft items.\\
As a result of certain actions, a character gains crafting experience progress.
When they reach 10 points of crafting experience progress, they gain 1 Crafting XP.\\
For scavenging the lands, a character gains 2 progress for each day (a total of four 4-hour intervals) that they have spent scavenging.
For butchering enemies, a character gains 1 progress for each encounter's worth of creatures they have harvested.\\
For crafting, a character gains 2 progress for each crafting action they have successfully taken, as long as their bonuses aren't so high that they couldn't have possibly failed the craft.
What a crafting action entails is dictated by the type of crafting a character performs.
For example, crafting a batch of potions counts as a crafting action for Alchemy, but for smithing, doing a days' work worth of crafting would be the crafting action.\\
\textbf{Note:} It should be stated that crafting at the game table is boring for most players.
Except in very limited situations, it is preferable if crafting checks happen after a game session, or between game sessions.