\section{Enchantments}\label{sec:enchantments}
The following section contains a list of enchantments.
Enchanted items can be crafted with the~\nameref{perk:enchanting} Perk, bought from certain, rare shops, or found.

\subsection{Weapon Enchantments}\label{subsec:enchantmentsWeapons}
These enchantments can be placed exclusively on weapons and projectiles.
A projectile typically loses its enchantment if it hits a target, even if the projectile is recovered afterward.
When enchanting projectiles, one enchantment recipe is enough for 20 tiny items, 10 small items or 5 medium items.

\subsubsection{Y Bane X}\label{enchantment:Bane}
When creating this enchantment, replace Y with a creature type descriptor.
The weapon deals Xd4 additional bane damage against creatures with that type descriptor, where X is the level of the enchantment.
For example, if a character performs a slash against a Goblin with a Longsword of Goblin Bane 1, the attack deals 3d6 + STR/AGI Cutting damage + 1d4 bane damage.

\subsubsection{Y Smiting}\label{enchantment:Smiting}
This enchantment can only be added to a weapon that has the "Bane" enchantment.
If that weapon can only have one enchantment, the Smiting enchantment replaces the Bane enchantment.
If the base weapon has multiple Bane enchantments, the Smiting enchantment applies to one of the Bane enchantments.
In a case where a weapon has both a Bane and a Smiting enchantments, both enchantments combined would be called a Hatred enchantment.
When landing a critical hit against a creature with the type descriptor of the Bane enchantment, you roll each die three times instead of two times.
For example, a Longsword of Goblin Smiting would deal 9d6 + STR/AGI on a Critical Slash against a Goblin, instead of 6d6 + STR/AGI.
If the Smiting enchantment has not replaced the Bane enchantment (i.e a Longsword of Goblin Hatred), the additional d4s from the Bane enchantment are also rolled 3 times.
For example, a Slash from a Longsword of Goblin Hatred 3 would deal 9d6 + STR/AGI cutting and 12d4 bane damage on a critical hit.

\subsubsection{Flaming X}\label{enchantment:Flaming}
A weapon with the Flaming enchantment deals an additional Xd4 heat damage, where X is the level of the enchantment.

\subsubsection{Frost X}\label{enchantment:Frost}
A weapon with the Frost enchantment deals an additional Xd4 cold damage, where X is the level of the enchantment.

\subsubsection{Shocking X}\label{enchantment:Shocking}
A weapon with the Shocking enchantment deals an additional Xd4 electrical damage, where X is the level of the enchantment.

\subsubsection{Radiating X}\label{enchantment:Radiating}
A weapon with the Radiating enchantment deals an additional Xd4 radiation damage, where X is the level of the enchantment.

\subsubsection{Corroding X}\label{enchantment:Corroding}
A weapon with the Corrding enchantment deals an additional Xd4 corrosion damage, where X is the level of the enchantment.

\subsubsection{Nihilating X}\label{enchantment:Nihilating}
A weapon with the Nihilating enchantment deals an additional Xd4 nihilation damage, where X is the level of the enchantment.

\subsubsection{Bursting X}\label{enchantment:Bursting}
This enchantment can only be added to a weapon that deals non-physical, e.g.\ heat, cold, electrical, radiation, corrosion or nihilation damage.
The damage must deal at least a minimum of X damage of that type for the enchantment, where X is the level of the Bursting enchantment.
For example, for a weapon to become a Heat Bursting 2 weapon, it would have to be able to deal 2, 2d4, 2d6, 2d8, 2d10, 2d12, 1d4+1,\ldots heat damage.
If only certain attacks of the weapon deal this type of non-physical damage, the Bursting effect only applies to these attacks.
If that weapon has gained the elemental damage from an enchantment and can only have one enchantment, the Bursting enchantment replaces that effect.
If the base weapon has multiple types of non-physical damage, the Bursting enchantment applies to one of these damage types.
When landing a critical hit with this weapon, the weapon deals (2 times X)d10 of the non-physical damage type of the Burst, where X is the level of the Bursting enchantment.

For example, a Flaming I weapon that becomes enchanted with the Bursting effect would become a Heat Bursting I weapon, dealing 2d10 heat damage on a critical hit.
If the flaming weapon could be enchanted with multiple enchantments, it would become a Flaming Heat Burst Weapon, dealing 2d4 heat damage regularly, and 4d4+2d10 heat damage on a critical hit.

\subsubsection{Ethereal}\label{enchantment:Etheral}
A weapon with the ethereal enchantment ignores the physical damage resistance that a target creature gains from being ethereal.

\subsubsection{Vampiric}\label{enchantment:Vampiric}
A weapon with the Vampiric enchantment heals the wielder by half the damage dealt with every attack.

\subsubsection{Ammunition Producing}\label{enchantment:AmmuProducing}
This enchantment can only be placed on a weapon with the Loading Action.
The weapon now magically produces a appropriate piece of ammunition when being shot without loading first.
The piece of ammunition disappears after being shot.
As a result, the weapon does not have to be loaded anymore.
However, it can still be loaded by non-summoned ammunition - for example, in order to use special or enchanted ammunition.

\subsubsection{Double Strike}\label{enchantment:DoubleStrike}
This enchantment can only be placed on weapons that deal piercing damage.
When making an attack with that weapon that would deal piercing damage, the weapon deals damage twice, as if the hit had happened twice.
If the attack was a critical hit, the second attack also counts as a critical hit.

\subsubsection{Eversharp}\label{enchantment:Eversharp}
This enchantment can only be placed on a weapon that deals slashing damage.
The enchanted weapon deals a critical hit on a natural 18, 19 and 20, instead of just a 20.
The weapon can not benefit from using a whetstone.

\subsubsection{Thundering}\label{enchantment:Thundering}
This enchantment can only be placed on a weapon that deals blunt damage.
When the weapon deals blunt damage, it also deals 1d4 AP damage.

\subsubsection{Bound}\label{enchantment:Bound}
This enchantment can not be placed on ammunition.
When creating this enchantment, choose a willing creature you can see, and a name for the weapon.
If the creature is already bound to a weapon with the same name, the enchantment fails, and all materials are lost.
The creature can summon the weapon from any place in the multiverse by speaking its name.
The weapon disappears from wherever it was before, and appears in the creature's hands, as if it had been drawn.
If there is no space for the weapon, it appears in the closest space with enough room for it.
If the creature dies, the weapon loses this enchantment.
