\section{Ingredients}\label{sec:ingredients}
These are items that can be found and harvested in order to create items.
They are ordered by type.\\
\\

\subsection{Alchemical solvents}\label{subsec:solvents}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | l}
	Name & Price (In Coins) & Effect\\ \hline
	Alcohol, cheap & 5 & Crafting Check -4\\
	Alcohol, mediocre & 10 & Crafting Check -2\\
	Alcohol, normal & 20 & Nothing\\
	Alcohol, fine & 50 & Crafting Check +2\\
	Alcohol, exquisite & 100 & Crafting Check +4\\
	Oil, cheap & 3 & Crafting Check -4\\
	Oil, mediocre & 7 & Crafting Check -2\\
	Oil, normal & 15 & Nothing\\
	Oil, fine & 40 & Crafting Check +2\\
	Oil, exquisite & 80 & Crafting Check +4\\
	Water, stale & - & Crafting Check -2\\
	Water, drinkable & -/1 & Nothing\\
	Water, spring & 5 & Crafting Check +2\\
	Water, distilled & 20 & Crafting Check +4\\
\end{longtable}

Prices for alcohol, oil and water don't include prices for bottles.
They are considered to be enough for one bottle, which equals 5 vials.
One vial full of alcohol, oil or water is needed for alchemical recipes. \\

The price for drinkable water depends on the area - buying the water from a tavern or a well-owner costs 1 Coins per bottle, but otherwise it might be considered free.\\


\subsection{Soul Shards}\label{subsec:soulShards}
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Shard & Size & Price (In Coins)\\ \hline
	Tiny & CS & 50\\
	Small & CS & 250\\
	Normal & T & 1,000\\
	Large & T & 5,000\\
	Massive & T & 10,000\\
	Huge & S & 50,000\\
	Radiant & T & 100,000\\
\end{longtable}


\subsection{Alchemical Ingredients}\label{subsec:alchemicalIngredients}
Alchemical Ingredients contain certain essences.
If a recipe requires a specific essence, any item that contains that essence can be used for that potion.
Some potions may require different ingredients with the same essence, or very specific items. \\

\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r}
	Name & Size & Price (In Coins)\\
	\hline
	\multicolumn{3}{c}{Tier 1}\\
	\hline
	Health Essence I & T & 20\\
	Body Essence I & T & 20\\
	Poison Essence I & T & 15\\
	Magic Essence I & T & 25\\
	Ice Essence I & T & 30\\
	Speed Essence I & T & 35\\
	Fire Essence I & T & 30\\
	Lightning Essence I & T & 35\\
	Radiant Essence I & T & 40\\
	Light Essence I & T & 30\\
	\hline
	\multicolumn{3}{c}{Tier 2}\\
	\hline
	Health Essence II & T & 60\\
	Body Essence II & T & 60\\
	Poison Essence II & T & 45\\
	Magic Essence II & T & 75\\
	Ice Essence II & T & 90\\
	Speed Essence II & T & 115\\
	Fire Essence II & T & 90\\
	Lightning Essence II & T & 115\\
	Radiant Essence II & T & 120\\
	Light Essence II & T & 90\\
\end{longtable}

\subsection{Cooking ingredients}\label{subsec:cookingIngredients}
This is a list of ingredients that can be used in recipes.
If a recipe calls for a specific type of ingredient, any ingredient with that type can be used.
The effect of that item are then applied to the resulting meals.
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r | l | p{3cm} }
	Name & Size & Price (In Coins) & Type & Effect\\ \hline
	Bread, stale & T & 1 & Carbohydrate & None\\
	Bread, normal & T & 2 & Carbohydrate & +1 Mana\\
	Bread, good & T & 3 & Carbohydrate & +2 Mana\\
	Salt, sea or rock & CS & 2 & Season & None\\
	Salt, high quality & CS & 5 & Season & +1d4 Motivation\\
	Cheese, cheap & T & 1 & Side & None\\
	Cheese, fresh & T & 2 & Side & +5 temp Stamina\\
	Cheese, hard & T & 3 & Side & +10 temp Stamina\\
	Cheese, high quality & T & 10 & Side & +20 temp Stamina\\
	Meat, beef & T & 5 & Protein & +1d4 Motivation\\
	Meat, pork & T & 3 & Protein & None \\
	Meat, wolf & T & 8 & Protein & +1d8 temp Health\\
	Meat, giant spider & T & 10 & Protein & Meal lasts +2 weeks\\
\end{longtable}

Whenever a meal effect would result in temporary Stamina, Health or Mana, or give motivation dice, this effect lasts for 8 hours, or until the next meal is consumed.
After that, the effect ends.
Temporary Health and Mana are consumed first, temporary Stamina is consumed last.
Neither can be replenished after being used.
Motivation dice can be added on any attribute check, including attack and defense rolls.
The character using the motivation can decide if and how many motivation dice are spent on one check before making the roll.
The dice are spent afterwards and cannot be used again.\\

\subsection{Scraps}\label{subsec:scraps}
These resources can be collected from monsters or the environment.
\rowcolors{2}{lightgray}{white}
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Wolf Fur Scraps & T & 2\\
	Leather Scraps & T & 1\\
	Bronze Scraps & T & 3\\
	Iron Scraps & T & 4\\
	Copper Scraps & T & 1\\
	Tin Scraps & T & 2\\
	Cloth Scraps & T & -\\
\end{longtable}

\subsection{Resources}\label{subsec:resources}
These resources can be bought or crafted from scraps and other resources.
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Name & Size & Price\\ \hline
	Feathers, 20 & T & 5\\
	Leather Fittings & S & 10\\
	Innards & T & 5\\
	Yarn & T & 10\\
	Metal Fittings & S & 50\\
	Nail & T & 5\\
\end{longtable}

\subsubsection{Yarn}
A spool of yarn has 10 charges.

\subsection{Hide}\label{subsec:hide}
These resources can be bought or crafted from scraps.
Hide is used in leatherworking.
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Hide (Fur) & M & 20\\
	Hide (Leather) & M & 50\\
	Hide (Wolf Fur) & M & 150\\
	Hide (Wolf Leather) & M & 250\\
\end{longtable}

\subsubsection{Fur}
Fur is created from the hide of goats, sheep or other domesticated creatures.\\
When used as the main ingredient for crafting armor, fur increases resistance to cold by 2.
If that armor would have Pockets, it halves the amount of pockets of the resulting item.
It also increases the Crafting Threshold by 2.

\subsubsection{Leather}
Leather is created by curing the hide of cows, goats, sheep or other domesticated creatures.\\
When used as the main ingredient for crafting armor, leather increases the base physical resistances of that armor by 1 each, as well as add (or increase) the resistance to heat and cold by 1.
It also increases the Recipe Tier by 1 and the Crafting Threshold by 5.

\subsubsection{Wolf Fur}
Fur from a wolf.\\
When used as the main ingredient for crafting armor, wolf fur increases physical resistance by 1 each, and resistance to cold by 4.
If that armor would have Pockets, it halves the amount of pockets of the resulting item.
It also increases the Recipe Tier by 2 and the Crafting Threshold by 8.

\subsubsection{Wolf Leather}
Wolf Leather is created by curing the hide of a wolf.\\
When used as the main ingredient for crafting armor, leather increases the base physical resistances of that armor by 2 each, as well as add (or increase) the resistance to heat and cold by 2.
It also increases the Recipe Tier by 2 and the Crafting Threshold by 8.

\subsection{Cloth}\label{subsec:cloth}
These resources can be bought or crafted from scraps.
Cloth is used in tailoring.
\begin{longtable}{l | r | r }
	Name & Size & Price\\ \hline
	Cloth (Linen) & M & 5\\
	Cloth (Fleece) & M & 15\\
\end{longtable}

\subsubsection{Linen}
Linen is a form of woven fibre from flax.\\
When used as the main ingredient for crafting armor, linen does not modify the base recipe.

\subsubsection{Fleece}
Fleece is the rough coat of wool-bearing animals, such as sheep.\\
When used as the main ingredient for crafting armor, fleece increases the physical resistances by 1 each, and increases resistance to cold by 1.
It also removes the Under Attribute.
It also increases the Crafting Threshold by 2.

\subsection{Ingots}\label{subsec:ingots}
These metal ingots can be used for weapons, armor and other items.
Whenever such a recipe allows for multiple ingots, they have to be of the same type.
The effects listed are applied to any weapon, armor or other item crafted with this metal, respectively if the recipe itself calls for "metal ingot".
\begin{longtable}{l | r | r | p{2cm} | p{2cm} | p{2cm}}
	Name & Weight & Price (In Coins)\\ \hline
	Bronze Ingot & T & 30 \\
	Iron Ingot & T & 60 \\
	Steel Ingot & T & 100 \\
	Mithril  Ingot & T (but weighs like CS) & 1,000\\
\end{longtable}

\subsubsection{Bronze}
Bronze is made by smelting 3 parts Copper and 1 part tin.\\
\textbf{Armor}
When used as the main ingredient in crafting armor, bronze does not modify the base recipe.\\
\textbf{Weapons}
When used as the main ingredient in crafting weapons, bronze does not modify the base recipe.

\subsubsection{Iron}
Iron is a light metal that is easy to forge.
However, it rusts easily and is not too hard.\\
\textbf{Armor}
When used as the main ingredient in crafting armor, iron increases the base physical resistances by 50\%.\\
It also increases the Crafting Threshold by 3.\\
\textbf{Weapons}
When used as the main ingredient in crafting weapons, iron does not modify the base recipe.

\subsubsection{Steel}
Steel is a form of iron that was purified and infused with carbon, making it harder and more resistant to corrosion.\\
\textbf{Armor}
When used as the main ingredient in crafting armor, steel increases the base physical resistances by 75\%.\\
It also increases the Recipe Tier by 1 and the Crafting Threshold by 7.\\
\textbf{Weapons}
When used as the main ingredient in crafting weapons, steel does not modify the base recipe.\\

\subsubsection{Mithril}
A very rare ingredient, mithril is a metal with silver colour and a blue sheen.
It is extremely light and flexible, while retaining incredible strength.\\
\textbf{Armor}
When used as the main ingredient in crafting armor, steel increases the base physical resistances by 75\%.
Additionally, a piece of mithril armor can be worn as if it was one armor type lighter (for example, a mithril half plate could be worn by someone who is proficient in medium armor only).
If a character has a higher proficiency for the heavier armor type, they can choose to use that instead.
Also, the maximum agility of a medium or heavy mithril armor is increased by 2.\\
It also increases the Recipe Tier by 2 and the Crafting Threshold by 10.\\
\textbf{Weapons}
When used as the main ingredient in crafting weapons, steel does not modify the base recipe.