\chapter{Cultures}\label{ch:cultures}
Every player character was raised in a certain environment which might not be directly linked to their species.
Choose one of these cultural backgrounds when creating a new character.
You gain a +1d6 skill bonus to social interactions with members of said culture.
Additionally, you also gain this bonus when recalling information about the culture, it's governments, history, legends, arts, crafts, the areas it is typically found in, and other checks related to that culture.

\begin{itemize}
    \item You were raised in \textbf{Wood Elven} society.
    You spent your days tracking animals, learning about the forests, and listening to the teachings of the trees.
    You were most likely taught hunting, lore about fauna and flora, and how to move unseen.
    You can also speak, write and read the Elven language.
    \item You were raised in \textbf{High Elven} society.
    You lived in one of the many alabaster cities and dined on the finest food in the lands.
    You were most likely taught poetry, magic and arts at a very young age.
    You can also speak, write and read the Elven language.
    \item You were raised in \textbf{Dark Elven} society.
    You grew up in a fortified cities of obsidian and iron underneath a granit sky.
    You were most likely taught about cavern ecology, followed the rigid traditions and hierarchies of Dark Elven society, and learned some form of martial combat.
    You can also speak, write and read the Dark Elven language.
    \item You were raised in \textbf{Dwarvish} society.
    You either grew up in one of the many mountain homes, or in one of the smaller hillside settlements.
    As a dwarf, learning a trade and how to defend your home was important to your people, and you probably can hold your liquor.
    You can also speak, write and read the Dwarven language.
    \item You were raised in \textbf{Orcish} society.
    You learned early, that the strong eat, mate and speak, while the weak hunger, are alone and hold their tongue.
    As such, you most likely can wield and axe, and a bow, and know how to stand up to those that try to put you down.
    You can also speak the Orcish language.
    \item You were raised in \textbf{Gnomish} society.
    You spend your days in tranquility, amongst small critters, eating vegetarian meals, and enjoying the gifts of nature.
    That, or you spent your days in a larger gnomish settlement, learning the ways of metal and glass and steam.
    You most likely either learned the ways of nature, becoming a gardener, or cook, or you learned how to tinker with small toys and gadgets.
    You can also speak, write and read the Gnomish language.
    \item You were raised in a \textbf{Midlands} society.
    The midlands are a mostly forested area, with rolling, grassy hills and farmsteads where civilization was able to carve out a humble, but fruitful livelihood.
    Dotted in between are the walled towns and castles of local lords and rulers, who busy themselves with keeping the citizens safe from the dangers of nature, and their neighbours.
    You can also speak, write and read one additional language of your choice.
    \item You were raised in a \textbf{Northern} society.
    In the North, rolling hills of grass and fields are replaced by more rugged and cold planes, strewn with large rocks moved by glaciers ages ago.
    You most likely learned to appreciate the taste of mead and fish, and berries and wild game.
    You can also speak, write and read one additional language of your choice.
    \item You were raised in a \textbf{Desert} society.
    You travelled the rolling dunes and rocky bluffs of the hot, arid lands of the world, and learned how to survive on the small water you found in the few oases on the way.
    You can also speak, write and read one additional language of your choice.
    \item You were raised in a \textbf{Bazaar} society
    You were born in a rich society of poets, traders, philosophers and magicians, that created a bustling society around one of the few permanent sources of water in an otherwise arid land.
    You can also speak, write and read one additional language of your choice.
    \item You were raised in a \textbf{Steppes} society.
    You travelled the eastern grasslands with your herds of pack animals, and learned how to ride horses (or potentially other beasts) at a very young age.
    You know how to track, fight - especially how to shoot a bow from a moving mount - and the importance of kinship and tradition has been taught to you from a young age.
    You can also speak, write and read one additional language of your choice.
    \item You were raised in an \textbf{Eastern} society.
    Your culture is rich, and full of amazing and great inventions.
    Your kings are guarded by the stewardship of great dragons and spirits, and your arts are manifold and fantastical.
    Your history is full of terrible battles, catastrophes, and famines.
    However, your culture has prevailed over the ages, producing philosophers, poets, artists, warrior monks, and futuristic feats of engineering.
    You can also speak, write and read one additional language of your choice.
\end{itemize}