\section{Guard}\label{background:guard}
Once a stalwart guardian of city streets, you've now embraced the adventurer's path.
Your loyalty to law and order remains, but the wider world calls.
Whether a sense of duty propels you or a yearning for change guides you, your experience in maintaining order equips you for the challenges beyond the city gates.

A quest for justice might lead you to confront criminal networks that span beyond your city's borders.
Conversely, you might embrace your authority to mediate conflicts and maintain order in new lands.
The allure of uncharted territories and unmet challenges beckons, while your past connections as a city guard can provide insight and support in unfamiliar environments.

Hidden motivations could be at play.
A personal vendetta might fuel your journey, or perhaps your loyalty to a higher power extends beyond city walls.
Regardless, your goals encompass upholding justice, adapting your enforcement skills to diverse situations, or even seeking personal redemption.

The path you tread echoes with the clank of armor and the determination of one who knows the labyrinthine streets of cities intimately.
Adventure becomes your new beat, where the law you've sworn to uphold extends into unexplored realms.
Will you be a beacon of honor, a lone enforcer of justice, or a symbol of transition, embodying the intricate balance between the familiar and the unknown?

\subsection{Statistics}
Choose either Deception, Intimidation, or Negotiation.
You gain a +1d4 experience bonus on checks regarding this type of interaction, as well as Examination.
