\chapter{Armor and Clothing}\label{ch:armor}
\section{Description}\label{armorDescription}
Every character can wear an armor or clothing.
Armor is ordered into 4 weight categories: Cloth, Light, Medium and Heavy.
A character wearing armor gains the resistances against Blunt, Cutting, and Piercing damage specified in the "Res" column.
Also, any armor can have multiple attributes, which are described below.\\
While wearing armor that a character is proficient in using, they may add their Level to their Dodge value.
If a character is not trained in that type of armor, they are unable to do so.
\subsection{Armor quality}\label{subsec:armorQuality}
Manufactured armor can have different qualities.
For example, an iron plate armor might be rusted or it might be masterfully crafted.
The quality bonus of cloth, or light armor adds a bonus to Dodge - this modifier ranges from --3 (broken) to +3 (high mastery craftsmanship).
The quality bonus of medium and heavy armor adds a bonus to block rolls - this modifier ranges from --3 (broken) to +3 (high mastery craftsmanship).
The quality bonus of an armor changes its base price:\\

\begin{itemize}
    \item Quality Bonus -3: Base Price * 1/4
    \item Quality Bonus -2: Base Price * 1/3
    \item Quality Bonus -1: Base Price * 1/2
    \item Quality Bonus 0: Base Price
    \item Quality Bonus +1: Base Price * 1.5
    \item Quality Bonus +2: Base Price * 2
    \item Quality Bonus +3: Base Price * 3
\end{itemize}

\section{Armor List}\label{armorList}

\luadirect{printArmorHead()}
\luadirect{printArmorOver("Clothing")}
\luadirect{printAllArmors('./gotfFantasy/inventory/equipment/armor/cloth')}
\luadirect{printArmorOver("Light")}
\luadirect{printAllArmors('./gotfFantasy/inventory/equipment/armor/light')}
\luadirect{printArmorOver("Medium")}
\luadirect{printAllArmors('./gotfFantasy/inventory/equipment/armor/medium')}
\luadirect{printArmorOver("Heavy")}
\luadirect{printAllArmors('./gotfFantasy/inventory/equipment/armor/heavy')}
\luadirect{printArmorFoot()}

\input{./gotfFantasy/inventory/equipment/armor/armorAttributes}
