\section{Armor Attributes}\label{sec:armorAttributes}

\subsection{Clothing}\label{subsec:clothing}
Clothing in itself does not count as armor, but it does grant Armor Reduction.

\subsection{Light Armor}\label{subsec:lightArmor}
Light armor is flexible and allows agile users to move around freely.
It can usually be donned and doffed in a matter of one or two minutes.
Leather, fur and very light, but also very expensive metals or metal chains are used to create light armor.
While wearing light armor, a character's Agility can not exceed 10.

\subsection{Medium Armor}\label{subsec:mediumArmor}
Medium Armor is a great balance between the strong defenses of heavy armor and the agility of light armor.
It is often made of cloth with strips of metal sewn in, or with leather pads.
It can also consist of overlapping slabs of metal or leather, giving the armor scales.
It takes 5 Minutes to don or remove medium armor.
While wearing medium armor, a character's Agility can not exceed 8.

\subsection{Heavy Armor}\label{subsec:heavyArmor}
Heavy Armor is slow and clunky, but also adds the biggest bonus to armor of any type.
It requires at least 10 minutes to don and doff such a piece of armor, and while wearing Heavy Armor, the wearer's Agility can not exceed a value of 6.

\subsection{Flammable}\label{armor:flammable}
An Armor with this attribute easily catches fire.
Whenever a character wearing it would take heat damage, the armor starts to burn.\\
Burning Armor can be put out by anyone who is able to touch it.
Doing so takes 4 AP.\\
Burning Armor is also extinguished when the wearer would take cold damage, or when it is doused in water.\\
If burning armor isn't put out by some other effect, it burns for 6 AP if it's cloth or light armor, 10 AP if it is medium or 14 AP if it is heavy.\\
While wearing a burning armor, the wearer takes 1 heat damage per AP that passes until it is put out.
Any armor that burned for at least 1 AP becomes damaged afterwards, losing all of its properties.

\subsection{Horrid}\label{armor:horrid}
An Armor with the horrid attribute has dark energies associated with it.
When the wearer of such armor takes necrose or psychic damage, they take an additional 3 damage from that damage source.

\subsection{Enchantable}\label{armor:enchantable}
An Armor that has this attribute can be enchanted a different amount than just once.
It can instead hold an amount of Enchantments by the number specified.
This means that any armor that doesn't have the "Enchantable" attribute specified has the "Enchantable 1".

\subsection{Lightweight}\label{armor:lightweight}
An Armor with the Leightweight attribute reduces the wearer's Agility as if it were one Weight class lower.
Additionally, if the wearer of said armor is more proficient in the lower weight class than the armor's actual weight class, they can benefit from the lower proficiency as if the armor was one weight class lower.

\subsection{Over and Under}\label{armor:under}
An armor with the "under" attribute can be worn under any "over" armor.\\
An armor with the "over" attribute can be worn over any "under" armor.\\
When both armors grant resistances to a damage type, do not add them together.
Instead, the larger respective resistance count.\\
Wearing two pieces of armor inflicts a -2 equipment malus to character's Agility.
This malus can not reduce a character's agility to less than 1.

\subsection{Pockets}\label{armor:pockets}
An armor with Pockets has the ability to hold a certain amount of items in its pockets.
For example, a piece of Armor might have "Pockets (4S)", which means that it can hold 4 small items.
These 4 small items are assumed to be divided into different pockets, like two regular trouser pockets, one breast pocket and one back pocket.